quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-06 paper-quollr.Rmd
Added colors according to the clusters

training_data_limb <- read_rds("data/limb_muscles/facs_limb_muscles_pcs_10.rds")
```

@@

# umap_limb_scaled_with_cluster <- umap_limb_scaled |>
#   mutate(cluster = umap_limb_scaled_with_cluster$cluster)

trimesh_removed_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled,
    aes(
      x = emb1,
      y = emb2
    ),
    alpha = 0.3,
    color = "#a65628"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  #scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

# data_limb_n <- data_limb |>
#   select(-type) |>
#   mutate(type = as.character(umap_limb_scaled_with_cluster$cluster))

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = distance_df_small_edges_limb$from,
                         lineTo = distance_df_small_edges_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("data", "model")),
                         levelColors = c("#a65628", "#000000"))
```

@@

# umap_limb_scaled_with_cluster <- umap_limb_scaled |>
#   mutate(cluster = umap_limb_scaled_with_cluster$cluster)

trimesh_removed_limb_best <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_best,
    aes(
      x = emb1,
      y = emb2
    ),
    alpha = 0.3,
    color = "#ff7f00"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  #scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

# data_limb_n <- data_limb |>
#   select(-type) |>
#   mutate(type = as.character(umap_limb_scaled_with_cluster$cluster))

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = distance_df_small_edges_limb$from,
                         lineTo = distance_df_small_edges_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("data", "model")),
                         levelColors = c("#ff7f00", "#000000"))
```

>>>>

training_data_limb <- read_rds("data/limb_muscles/facs_limb_muscles_pcs_10.rds")

cluster_df <- read_rds("data/limb_muscles/facs_limb_muscles_cluster_df.rds")
```

@@

tsne_limb_scaled_with_cluster <- inner_join(tsne_limb_scaled, cluster_df, by = "ID") |>
  mutate(cluster.ids = as.character(cluster.ids))

trimesh_removed_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster.ids
    ),
    alpha = 0.3#,
    #color = "#a65628"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

data_limb_n <- data_limb |>
  select(-type) |>
  mutate(type = as.character(tsne_limb_scaled_with_cluster$cluster.ids))

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb_n)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = distance_df_small_edges_limb$from,
                         lineTo = distance_df_small_edges_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"))
```

@@

tsne_limb_scaled_best_with_cluster <- inner_join(tsne_limb_scaled_best, cluster_df, by = "ID") |>
  mutate(cluster.ids = as.character(cluster.ids))

trimesh_removed_limb_best <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_best_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster.ids
    ),
    alpha = 0.3#,
    #color = "#ff7f00"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb_n)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = distance_df_small_edges_limb$from,
                         lineTo = distance_df_small_edges_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"))
```
